---
title: 'Memo: Value Allocation Response'
author: "Johnson"
date: "9/18/2019"
header-includes:
  - \usepackage{booktabs}
output: 
  pdf_document:
    keep_tex: true
    md_extensions: +raw_attribute
---    
    
    
```{r setup, include=FALSE, cache=FALSE}
library(data.table)
library(xtable)
library(kableExtra)
knitr::opts_chunk$set(echo = FALSE)
```

# Background

This memo describes the auction emotion responses to the value allocation.

Analysis is as follows:

1. Emotional response to value allocation (not controlling for value) for 1, 2, 3, 4 seconds after the value allocation. (Including aggregate and snapshot seconds)
2. Emotional response to value allocation by Value quartile (and seconds in 1)
3. Emotional response to vlaue allocation regression with individual fixed effects.

# Emotion response to value allocation

These are tables.

```{r}
if(!file.exists('~/Dropbox/pkg.data/auction_emotions/l_dt_emotions_first.rds')){
  dt_seconds <- readRDS('~/Dropbox/pkg.data/auction_emotions/Clean/dt_seconds.rds')
  l_seconds_dts <- list()
  
  l_seconds_dts$a_second0 <- dt_seconds[MarkerType=='auction' & marker_sec_elapsed == 0 & !is.na(Score_num)]
  l_seconds_dts$b_second1 <- dt_seconds[MarkerType=='auction' & marker_sec_elapsed == 1 & !is.na(Score_num)]
  l_seconds_dts$c_second2 <- dt_seconds[MarkerType=='auction' &
                                          marker_sec_elapsed == 2 &
                                          !is.na(Score_num)]
  l_seconds_dts$d_second3 <- dt_seconds[MarkerType=='auction' &
                                          marker_sec_elapsed == 3 &
                                          !is.na(Score_num)]
  #l_seconds_dts$e_second4 <- dt_seconds[MarkerType=='auction' &
  #                                        marker_sec_elapsed == 4 &
  #                                        !is.na(Score_num)]
  
  l_seconds_dts$f_secondlt2 <- dt_seconds[MarkerType=='auction' &
                                            marker_sec_elapsed <= 1 &
                                            !is.na(Score_num)][,Score_num:=mean(Score_num), 
                                                               by=.(AuctionType, AuctionNumber, EmotionType, participant_id)]
  l_seconds_dts$g_secondlt3 <- dt_seconds[MarkerType=='auction' &
                                            marker_sec_elapsed <= 2 &
                                            !is.na(Score_num)][,Score_num:=mean(Score_num), 
                                                               by=.(AuctionType, AuctionNumber, EmotionType, participant_id)]
  l_seconds_dts$h_secondlt4 <- dt_seconds[MarkerType=='auction' &
                                            marker_sec_elapsed <= 3 &
                                            !is.na(Score_num)][,Score_num:=mean(Score_num),
                                                               by=.(AuctionType, AuctionNumber, EmotionType, participant_id)]
 # l_seconds_dts$i_secondlt5 <- dt_seconds[MarkerType=='auction' &
 #                                           marker_sec_elapsed <= 4 &
 #                                           !is.na(Score_num)][,Score_num:=mean(Score_num),
 #                                                              by=.(AuctionType, AuctionNumber, EmotionType, participant_id)]
  #l_seconds_dts$e_second_one <- dt_seconds[MarkerType=='auction' &
  #                                                 marker_sec_elapsed <= 1 &
  #                                                 !is.na(Score_num)]
  
  # Create t-test
  emotions <- unique(l_seconds_dts[[1]]$EmotionType)
  auction_types <- unique(l_seconds_dts[[1]]$AuctionType)
  combs <- expand.grid(auction_types, auction_types, names(l_seconds_dts), names(l_seconds_dts), stringsAsFactors = FALSE)
  combs <- as.data.table(combs)
  names(combs) <- c('auction1', 'auction2', 'time1', 'time2')
  combs <- combs[auction1 != auction2]
  combs <- combs[auction1 %in% 'first_price' & auction2 %in% 'dutch']
  l_combs <- list()
  for(iComb in 1:nrow(combs)){
    dt_1 <- l_seconds_dts[[which(names(l_seconds_dts)==combs[iComb]$time1)]]
    dt_1 <- dt_1[AuctionType == combs[iComb]$auction1]
    dt_2 <- l_seconds_dts[[which(names(l_seconds_dts)==combs[iComb]$time2)]]
    dt_2 <- dt_2[AuctionType == combs[iComb]$auction2]
    l_emotions <- list()
    for(iEmotion in 1:length(emotions)){
      sEmotion <- emotions[iEmotion]
      dt_1_emotion_score <- dt_1[EmotionType %in% sEmotion]
      dt_2_emotion_score <- dt_2[EmotionType %in% sEmotion]
      t_test <- t.test(dt_1_emotion_score$Score_num, dt_2_emotion_score$Score_num, var.equal = FALSE)
      dt_ttest <- data.table(auction_1 = combs[iComb]$auction1,
                             time_obs_1 = combs[iComb]$time1,
                             auction_2 = combs[iComb]$auction2,
                             time_obs_2 = combs[iComb]$time2,
                             emotion = sEmotion,
                             mean_auction_1 = t_test$estimate[1],
                             mean_auction_2 = t_test$estimate[2],
                             t_stat = t_test$statistic,
                             p_value = t_test$p.value)
      dt_tttest <- dt_ttest[,auction_1_pct_auction_2 := ((mean_auction_1-mean_auction_2)/mean_auction_2)]
      l_emotions[[iEmotion]] <- dt_ttest
    }
    dt_emotions <- rbindlist(l_emotions, use.names = TRUE, fill=TRUE)
    l_combs[[iComb]] <- dt_emotions
  }
  dt_combs <- rbindlist(l_combs, use.names = TRUE, fill = TRUE)
  
  # Create tables to plot over
  
  l_dt_emotions <- list()
  for(iEmotion in 1:length(emotions)){
    sEmotion <- emotions[iEmotion]
    l_dt_emotions[[iEmotion]] <- dt_combs[emotion %in% sEmotion]
    dt <- l_dt_emotions[[iEmotion]]
    dt <- dt[order(-auction_1, time_obs_1, -auction_2, time_obs_2)]
    dt <- dt[, pstars:='']
    dt <- dt[p_value <= 0.01, pstars:='***']
    dt <- dt[p_value > 0.01 & p_value <= 0.05, pstars:='**']
    dt <- dt[p_value > 0.05 & p_value <= 0.10, pstars:='*']
    dt <- dt[ , s_val:=paste0(round(auction_1_pct_auction_2, 3), pstars)]
    dt <- dt[, s_val:=stringr::str_pad(s_val, 9, side='right', pad=' ')]
    dt_cast <- dcast(dt, auction_1 + time_obs_1 ~ auction_2 + time_obs_2, value.var='s_val')
    dt_cast <- dt_cast[, time_obs_1:=stringr::str_replace_all(time_obs_1, '(^[a-i]{1,1}\\_second)', '')]
    new_col_names <- sapply(names(dt_cast), function(x) stringr::str_replace(x, '(^dutch\\_[a-i]{1,1}\\_second)', ''))
    setnames(dt_cast, names(dt_cast), new_col_names)
    dt_cast$auction_1 <- NULL
    dt_cast$row_names <- c('$0-1$', '$1-2$', '$2-3$', '$3-4$', '$\\leq 2$' , '$\\leq 3$',  '$\\leq 4$')
    dt_cast <- dt_cast[, .(`row_names`, `0`, `1`, `2`, `3`, `lt2`, `lt3`, `lt4`)]
    setnames(dt_cast, 'row_names', '')
    l_dt_emotions[[iEmotion]] <- dt_cast
  }
  names(l_dt_emotions) <- emotions
  saveRDS(l_dt_emotions, '~/Dropbox/pkg.data/auction_emotions/l_dt_emotions_first.rds')
} else {
  l_dt_emotions <- readRDS('~/Dropbox/pkg.data/auction_emotions/l_dt_emotions_first.rds')
  emotions <- names(l_dt_emotions)
}
## Latex table output
captions_text <- ' emotional response of value allocation by time'
captions <- paste0(emotions, captions_text)

l_body <- NULL
l_body <- list()

l_table <- list()
l_header_list <- as.character()
l_header_list[1] <- '\\begin{table}[!htb] \n'
l_header_list[2] <- '\\caption{Emotional Response to Value Allocation: Auction Type and Time Analysis (part 1/2)} \n'
l_header_list[3] <- '\\label{tab:emotionalResponse2} \n'
l_header_list[4] <- '\\centering \n'
l_header_list[5] <- '\\begingroup \n'
l_header_list[6] <- '\\scriptsize \n'
l_header_list[7] <- '\\begin{tabular}{lrrrrrrr} \n'
l_header_list[8] <- '\\toprule'
l_header_list[9] <- '\\emph{First Price} & \\multicolumn{7}{c}{\\emph{Dutch}} \\\\ \n'
l_header_list[10] <- '\\cmidrule(lr){2-8} \n & $0-1$ & $1-2$ & $2-3$ & $3-4$ & $\\leq 2$ & $\\leq 3$ & $\\leq 4$ \\\\ \n'  

l_table$header <- l_header_list

l_body <- list()
for(i in 1:5){
  body_header <- character()
  body_header[1] <- '\\cmidrule(lr){2-8} \n'
  body_header[2] <- paste0('& \\multicolumn{7}{c}{\\emph{Panel ', stringr::str_to_upper(letters[i]),
                           ': ', emotions[i], '}}\\\\ \n')
  body_header[3] <- '\\cmidrule(lr){1-1} \\cmidrule(lr){2-8}'
  
  body <- character()
  body <- print.xtable(xtable(l_dt_emotions[[i]], format='latex'), include.rownames=FALSE, sep='\n', print.results = FALSE)
  body <- as.character(stringr::str_split(body, '\\n', simplify = FALSE)[[1]])
  body <- body[c(9:15)]
  body <- stringr::str_replace_all(body, '\\\\(?=\\$)', '')
  body <- stringr::str_replace_all(body, '.+(?=leq)', '$\\\\')
  l_body[[i]] <- c(body_header, body)
}
  
l_table$body <- l_body  

body_footer <- character()
body_footer[1] <- '\\bottomrule \n'
body_footer[2] <- '\\end{tabular} \n'
body_footer[3] <- '\\begin{minipage}{\\textwidth}'
body_footer[4] <- '\\footnotesize'
body_footer[5] <- '\\vspace{0.25cm}'
body_footer[6] <- '\\emph{Notes:} Table Values represent (mean(first price emotion score)-mean(dutch emotion score))/mean(dutch emotion score). ***, **, *, for p-values of 0.01, 0.05, 0.10 for the hypothesis test that mean(first price emotion score)=mean(dutch emotion score)'
body_footer[7] <- '\\end{minipage}'
body_footer[8] <- '\\endgroup'
body_footer[9] <- '\\end{table}'

l_table$body_footer <- body_footer
table_out <- unlist(l_table)
knitr::raw_latex(table_out)

l_body <- NULL
l_body <- list()

l_table <- list()
l_header_list <- as.character()
l_header_list[1] <- '\\begin{table}[!htb] \n'
l_header_list[2] <- '\\caption{Emotional Response to Value Allocation: Auction Type and Time Analysis (part 2/2)} \n'
l_header_list[3] <- '\\label{tab:emotionalResponse} \n'
l_header_list[4] <- '\\centering \n'
l_header_list[5] <- '\\begingroup \n'
l_header_list[6] <- '\\scriptsize \n'
l_header_list[7] <- '\\begin{tabular}{lrrrrrrr} \n'
l_header_list[8] <- '\\toprule'
l_header_list[9] <- '\\emph{First Price} & \\multicolumn{7}{c}{\\emph{Dutch}} \\\\ \n'
l_header_list[10] <- '\\cmidrule(lr){2-8} \n & $0-1$ & $1-2$ & $2-3$ & $3-4$ & $\\leq 2$ & $\\leq 3$ & $\\leq 4$ \\\\ \n'  

l_table$header <- l_header_list

l_body <- list()
for(i in 6:length(captions)){
  body_header <- character()
  body_header[1] <- '\\cmidrule(lr){2-8} \n'
  body_header[2] <- paste0('& \\multicolumn{7}{c}{\\emph{Panel ', stringr::str_to_upper(letters[i]),
                           ': ', emotions[i], '}}\\\\ \n')
  body_header[3] <- '\\cmidrule(lr){1-1} \\cmidrule(lr){2-8}'
  
  body <- character()
  body <- print.xtable(xtable(l_dt_emotions[[i]], format='latex'), include.rownames=FALSE, sep='\n', print.results = FALSE)
  body <- as.character(stringr::str_split(body, '\\n', simplify = FALSE)[[1]])
  body <- body[c(9:15)]
  body <- stringr::str_replace_all(body, '\\\\(?=\\$)', '')
  body <- stringr::str_replace_all(body, '.+(?=leq)', '$\\\\')
  l_body[[i]] <- c(body_header, body)
}
  
l_table$body <- l_body  

body_footer <- character()
body_footer[1] <- '\\bottomrule \n'
body_footer[2] <- '\\end{tabular} \n'
body_footer[3] <- '\\begin{minipage}{\\textwidth}'
body_footer[4] <- '\\footnotesize'
body_footer[5] <- '\\vspace{0.25cm}'
body_footer[6] <- '\\emph{Notes:} Table Values represent  (mean(first price emotion score)-mean(dutch emotion score))/mean(dutch emotion score). ***, **, *, for p-values of 0.01, 0.05, 0.10 for the hypothesis test that mean(first price emotion score)=mean(dutch emotion score)'
body_footer[7] <- '\\end{minipage}'
body_footer[8] <- '\\endgroup'
body_footer[9] <- '\\end{table}'

l_table$body_footer <- body_footer
table_out <- unlist(l_table)
knitr::raw_latex(table_out)


```

# Emotional response to the end of the auction (transition phase)

```{r dt_emotions_response_results}
dt_emotions_response_results_location <- '~/Dropbox/pkg.data/auction_emotions/l_dt_emotions_response_results.rds'
if(!file.exists(dt_emotions_response_results_location)){
  # Feedback (results 2 seconds or less out)
  dt_seconds <- readRDS('~/Dropbox/pkg.data/auction_emotions/Clean/dt_seconds.rds')
  l_seconds_dts <- list()
  
  l_seconds_dts$a_second0 <- dt_seconds[((AuctionType=='dutch' & MarkerType=='transition')|(AuctionType=='first_price' & MarkerType=='info')) &
                                          marker_sec_elapsed == 0 & !is.na(Score_num)]
  l_seconds_dts$b_second1 <- dt_seconds[((AuctionType=='dutch' & MarkerType=='transition')|(AuctionType=='first_price' & MarkerType=='info')) &
                                          marker_sec_elapsed == 1 & !is.na(Score_num)]
  l_seconds_dts$c_second2 <- dt_seconds[((AuctionType=='dutch' & MarkerType=='transition')|(AuctionType=='first_price' & MarkerType=='info')) &
                                          marker_sec_elapsed == 2 &
                                          !is.na(Score_num)]
  l_seconds_dts$d_second3 <- dt_seconds[((AuctionType=='dutch' & MarkerType=='transition')|(AuctionType=='first_price' & MarkerType=='info')) &
                                          marker_sec_elapsed == 3 &
                                          !is.na(Score_num)]
  l_seconds_dts$f_secondlt2 <- dt_seconds[((AuctionType=='dutch' & MarkerType=='transition')|(AuctionType=='first_price' & MarkerType=='info')) &
                                            marker_sec_elapsed <= 1 &
                                            !is.na(Score_num)][,Score_num:=mean(Score_num), 
                                                               by=.(AuctionType, AuctionNumber, EmotionType, participant_id)]
  l_seconds_dts$g_secondlt3 <- dt_seconds[((AuctionType=='dutch' & MarkerType=='transition')|(AuctionType=='first_price' & MarkerType=='info')) &
                                            marker_sec_elapsed <= 2 &
                                            !is.na(Score_num)][,Score_num:=mean(Score_num), 
                                                               by=.(AuctionType, AuctionNumber, EmotionType, participant_id)]
  l_seconds_dts$h_secondlt4 <- dt_seconds[((AuctionType=='dutch' & MarkerType=='transition')|(AuctionType=='first_price' & MarkerType=='info')) &
                                            marker_sec_elapsed <= 3 &
                                            !is.na(Score_num)][,Score_num:=mean(Score_num),
                                                               by=.(AuctionType, AuctionNumber, EmotionType, participant_id)]
  
  emotions <- unique(l_seconds_dts[[1]]$EmotionType)
  auction_types <- unique(l_seconds_dts[[1]]$AuctionType)
  combs <- expand.grid(auction_types, auction_types, names(l_seconds_dts), names(l_seconds_dts), stringsAsFactors = FALSE)
  combs <- as.data.table(combs)
  names(combs) <- c('auction1', 'auction2', 'time1', 'time2')
  combs <- combs[auction1 != auction2]
  combs <- combs[auction1 %in% 'first_price' & auction2 %in% 'dutch']
  l_combs <- list()
  for(iComb in 1:nrow(combs)){
    dt_1 <- l_seconds_dts[[which(names(l_seconds_dts)==combs[iComb]$time1)]]
    dt_1 <- dt_1[AuctionType == combs[iComb]$auction1]
    dt_2 <- l_seconds_dts[[which(names(l_seconds_dts)==combs[iComb]$time2)]]
    dt_2 <- dt_2[AuctionType == combs[iComb]$auction2]
    l_emotions <- list()
    for(iEmotion in 1:length(emotions)){
      sEmotion <- emotions[iEmotion]
      dt_1_emotion_score <- dt_1[EmotionType %in% sEmotion]
      dt_2_emotion_score <- dt_2[EmotionType %in% sEmotion]
      t_test <- t.test(dt_1_emotion_score$Score_num, dt_2_emotion_score$Score_num, var.equal = FALSE)
      dt_ttest <- data.table(auction_1 = combs[iComb]$auction1,
                             time_obs_1 = combs[iComb]$time1,
                             auction_2 = combs[iComb]$auction2,
                             time_obs_2 = combs[iComb]$time2,
                             emotion = sEmotion,
                             mean_auction_1 = t_test$estimate[1],
                             mean_auction_2 = t_test$estimate[2],
                             t_stat = t_test$statistic,
                             p_value = t_test$p.value)
      dt_tttest <- dt_ttest[,auction_1_pct_auction_2 := ((mean_auction_1-mean_auction_2)/mean_auction_2)]
      l_emotions[[iEmotion]] <- dt_ttest
    }
    dt_emotions <- rbindlist(l_emotions, use.names = TRUE, fill=TRUE)
    l_combs[[iComb]] <- dt_emotions
  }
  dt_combs <- rbindlist(l_combs, use.names = TRUE, fill = TRUE)
  
  # Create tables to plot over
  
  l_dt_emotions <- list()
  for(iEmotion in 1:length(emotions)){
    sEmotion <- emotions[iEmotion]
    l_dt_emotions[[iEmotion]] <- dt_combs[emotion %in% sEmotion]
    dt <- l_dt_emotions[[iEmotion]]
    dt <- dt[order(-auction_1, time_obs_1, -auction_2, time_obs_2)]
    dt <- dt[, pstars:='']
    dt <- dt[p_value <= 0.01, pstars:='***']
    dt <- dt[p_value > 0.01 & p_value <= 0.05, pstars:='**']
    dt <- dt[p_value > 0.05 & p_value <= 0.10, pstars:='*']
    dt <- dt[ , s_val:=paste0(round(auction_1_pct_auction_2, 3), pstars)]
    dt <- dt[, s_val:=stringr::str_pad(s_val, 9, side='right', pad=' ')]
    dt_cast <- dcast(dt, auction_1 + time_obs_1 ~ auction_2 + time_obs_2, value.var='s_val')
    dt_cast <- dt_cast[, time_obs_1:=stringr::str_replace_all(time_obs_1, '(^[a-i]{1,1}\\_second)', '')]
    new_col_names <- sapply(names(dt_cast), function(x) stringr::str_replace(x, '(^dutch\\_[a-i]{1,1}\\_second)', ''))
    setnames(dt_cast, names(dt_cast), new_col_names)
    dt_cast$auction_1 <- NULL
    dt_cast$row_names <- c('$0-1$', '$1-2$', '$2-3$', '$3-4$', '$\\leq 2$' , '$\\leq 3$',  '$\\leq 4$')
    dt_cast <- dt_cast[, .(`row_names`, `0`, `1`, `2`, `3`, `lt2`, `lt3`, `lt4`)]
    setnames(dt_cast, 'row_names', '')
    l_dt_emotions[[iEmotion]] <- dt_cast
  }
  names(l_dt_emotions) <- emotions
  saveRDS(l_dt_emotions, dt_emotions_response_results_location)
} else {
  l_dt_emotions <- readRDS(dt_emotions_response_results_location)
  emotions <- names(l_dt_emotions)
}
## Latex table output
captions_text <- ' emotional response of value allocation by time'
captions <- paste0(emotions, captions_text)

l_body <- NULL
l_body <- list()

l_table <- list()
l_header_list <- as.character()
l_header_list[1] <- '\\begin{table}[!htb] \n'
l_header_list[2] <- '\\caption{Emotional Response to Auction Finish: Auction Type and Time Analysis (part 1/2)} \n'
l_header_list[3] <- '\\label{tab:emotionalResponse2} \n'
l_header_list[4] <- '\\centering \n'
l_header_list[5] <- '\\begingroup \n'
l_header_list[6] <- '\\scriptsize \n'
l_header_list[7] <- '\\begin{tabular}{lrrrrrrr} \n'
l_header_list[8] <- '\\toprule'
l_header_list[9] <- '\\emph{First Price} & \\multicolumn{7}{c}{\\emph{Dutch}} \\\\ \n'
l_header_list[10] <- '\\cmidrule(lr){2-8} \n & $0-1$ & $1-2$ & $2-3$ & $3-4$ & $\\leq 2$ & $\\leq 3$ & $\\leq 4$ \\\\ \n'  

l_table$header <- l_header_list

l_body <- list()
for(i in 1:5){
  body_header <- character()
  body_header[1] <- '\\cmidrule(lr){2-8} \n'
  body_header[2] <- paste0('& \\multicolumn{7}{c}{\\emph{Panel ', stringr::str_to_upper(letters[i]),
                           ': ', emotions[i], '}}\\\\ \n')
  body_header[3] <- '\\cmidrule(lr){1-1} \\cmidrule(lr){2-8}'
  
  body <- character()
  body <- print.xtable(xtable(l_dt_emotions[[i]], format='latex'), include.rownames=FALSE, sep='\n', print.results = FALSE)
  body <- as.character(stringr::str_split(body, '\\n', simplify = FALSE)[[1]])
  body <- body[c(9:15)]
  body <- stringr::str_replace_all(body, '\\\\(?=\\$)', '')
  body <- stringr::str_replace_all(body, '.+(?=leq)', '$\\\\')
  l_body[[i]] <- c(body_header, body)
}

l_table$body <- l_body  

body_footer <- character()
body_footer[1] <- '\\bottomrule \n'
body_footer[2] <- '\\end{tabular} \n'
body_footer[3] <- '\\begin{minipage}{\\textwidth}'
body_footer[4] <- '\\footnotesize'
body_footer[5] <- '\\vspace{0.25cm}'
body_footer[6] <- '\\emph{Notes:} Table Values represent (mean(first price emotion score)-mean(dutch emotion score))/mean(dutch emotion score). ***, **, *, for p-values of 0.01, 0.05, 0.10 for the hypothesis test that mean(first price emotion score)=mean(dutch emotion score)'
body_footer[7] <- '\\end{minipage}'
body_footer[8] <- '\\endgroup'
body_footer[9] <- '\\end{table}'

l_table$body_footer <- body_footer
table_out <- unlist(l_table)
knitr::raw_latex(table_out)

l_body <- NULL
l_body <- list()

l_table <- list()
l_header_list <- as.character()
l_header_list[1] <- '\\begin{table}[!htb] \n'
l_header_list[2] <- '\\caption{Emotional Response to Auction Finish: Auction Type and Time Analysis (part 2/2)} \n'
l_header_list[3] <- '\\label{tab:emotionalResponse} \n'
l_header_list[4] <- '\\centering \n'
l_header_list[5] <- '\\begingroup \n'
l_header_list[6] <- '\\scriptsize \n'
l_header_list[7] <- '\\begin{tabular}{lrrrrrrr} \n'
l_header_list[8] <- '\\toprule'
l_header_list[9] <- '\\emph{First Price} & \\multicolumn{7}{c}{\\emph{Dutch}} \\\\ \n'
l_header_list[10] <- '\\cmidrule(lr){2-8} \n & $0-1$ & $1-2$ & $2-3$ & $3-4$ & $\\leq 2$ & $\\leq 3$ & $\\leq 4$ \\\\ \n'  

l_table$header <- l_header_list

l_body <- list()
for(i in 6:length(captions)){
  body_header <- character()
  body_header[1] <- '\\cmidrule(lr){2-8} \n'
  body_header[2] <- paste0('& \\multicolumn{7}{c}{\\emph{Panel ', stringr::str_to_upper(letters[i]),
                           ': ', emotions[i], '}}\\\\ \n')
  body_header[3] <- '\\cmidrule(lr){1-1} \\cmidrule(lr){2-8}'
  
  body <- character()
  body <- print.xtable(xtable(l_dt_emotions[[i]], format='latex'), include.rownames=FALSE, sep='\n', print.results = FALSE)
  body <- as.character(stringr::str_split(body, '\\n', simplify = FALSE)[[1]])
  body <- body[c(9:15)]
  body <- stringr::str_replace_all(body, '\\\\(?=\\$)', '')
  body <- stringr::str_replace_all(body, '.+(?=leq)', '$\\\\')
  l_body[[i]] <- c(body_header, body)
}

l_table$body <- l_body  

body_footer <- character()
body_footer[1] <- '\\bottomrule \n'
body_footer[2] <- '\\end{tabular} \n'
body_footer[3] <- '\\begin{minipage}{\\textwidth}'
body_footer[4] <- '\\footnotesize'
body_footer[5] <- '\\vspace{0.25cm}'
body_footer[6] <- '\\emph{Notes:} Table Values represent  (mean(first price emotion score)-mean(dutch emotion score))/mean(dutch emotion score). ***, **, *, for p-values of 0.01, 0.05, 0.10 for the hypothesis test that mean(first price emotion score)=mean(dutch emotion score)'
body_footer[7] <- '\\end{minipage}'
body_footer[8] <- '\\endgroup'
body_footer[9] <- '\\end{table}'

l_table$body_footer <- body_footer
table_out <- unlist(l_table)
knitr::raw_latex(table_out)

```



# Emotional response to the end of the auction by winner in the money loser in the money(transition phase)

## In the money by auction type

```{r in_the_money_by_auction_type}
if(!file.exists('~/Dropbox/pkg.data/auction_emotions/in_the_money.rds')){
  dt_seconds <- readRDS('~/Dropbox/pkg.data/auction_emotions/Clean/dt_seconds.rds')
  dt_in_the_money <- dt_seconds[, .SD[1], by=.(participant_id, AuctionType, AuctionNumber)]
  saveRDS(dt_in_the_money, '~/Dropbox/pkg.data/auction_emotions/in_the_money.rds')
} else {
  dt_in_the_money <- readRDS('~/Dropbox/pkg.data/auction_emotions/in_the_money.rds')
  dt_spread <- dcast(dt_in_the_money, Result~AuctionType, length)
}
```

```{r dt_emotions_in_the_money}
dt_emotions_in_the_money_location <- '~/Dropbox/pkg.data/auction_emotions/l_dt_emotions_in_the_money.rds'
if(!file.exists(dt_emotions_in_the_money_location)){
  # Feedback (results 2 seconds or less out)
  dt_seconds <- readRDS('~/Dropbox/pkg.data/auction_emotions/Clean/dt_seconds.rds')
        

  

  l_seconds_dts <- list()

    
  l_seconds_dts$a_second0 <- dt_seconds[((AuctionType=='dutch' & MarkerType=='transition')|(AuctionType=='first_price' & MarkerType=='info')) &
                                          marker_sec_elapsed == 0 & !is.na(Score_num)]
  l_seconds_dts$b_second1 <- dt_seconds[((AuctionType=='dutch' & MarkerType=='transition')|(AuctionType=='first_price' & MarkerType=='info')) &
                                          marker_sec_elapsed == 1 & !is.na(Score_num)]
  l_seconds_dts$c_second2 <- dt_seconds[((AuctionType=='dutch' & MarkerType=='transition')|(AuctionType=='first_price' & MarkerType=='info')) &
                                          marker_sec_elapsed == 2 &
                                          !is.na(Score_num)]
  l_seconds_dts$d_second3 <- dt_seconds[((AuctionType=='dutch' & MarkerType=='transition')|(AuctionType=='first_price' & MarkerType=='info')) &
                                          marker_sec_elapsed == 3 &
                                          !is.na(Score_num)]
  l_seconds_dts$f_secondlt2 <- dt_seconds[((AuctionType=='dutch' & MarkerType=='transition')|(AuctionType=='first_price' & MarkerType=='info')) &
                                            marker_sec_elapsed <= 1 &
                                            !is.na(Score_num)][,Score_num:=mean(Score_num), 
                                                               by=.(AuctionType, AuctionNumber, EmotionType, participant_id)]
  l_seconds_dts$g_secondlt3 <- dt_seconds[((AuctionType=='dutch' & MarkerType=='transition')|(AuctionType=='first_price' & MarkerType=='info')) &
                                            marker_sec_elapsed <= 2 &
                                            !is.na(Score_num)][,Score_num:=mean(Score_num), 
                                                               by=.(AuctionType, AuctionNumber, EmotionType, participant_id)]
  l_seconds_dts$h_secondlt4 <- dt_seconds[((AuctionType=='dutch' & MarkerType=='transition')|(AuctionType=='first_price' & MarkerType=='info')) &
                                            marker_sec_elapsed <= 3 &
                                            !is.na(Score_num)][,Score_num:=mean(Score_num),
                                                               by=.(AuctionType, AuctionNumber, EmotionType, participant_id)]
  
  emotions <- unique(l_seconds_dts[[1]]$EmotionType)
  auction_types <- unique(l_seconds_dts[[1]]$AuctionType)
  combs <- expand.grid(auction_types, auction_types, names(l_seconds_dts), names(l_seconds_dts), stringsAsFactors = FALSE)
  combs <- as.data.table(combs)
  names(combs) <- c('auction1', 'auction2', 'time1', 'time2')
  combs <- combs[auction1 != auction2]
  combs <- combs[auction1 %in% 'first_price' & auction2 %in% 'dutch']
  l_combs <- list()
  for(iComb in 1:nrow(combs)){
    dt_1 <- l_seconds_dts[[which(names(l_seconds_dts)==combs[iComb]$time1)]]
    dt_1 <- dt_1[AuctionType == combs[iComb]$auction1]
    dt_2 <- l_seconds_dts[[which(names(l_seconds_dts)==combs[iComb]$time2)]]
    dt_2 <- dt_2[AuctionType == combs[iComb]$auction2]
    l_emotions <- list()
    for(iEmotion in 1:length(emotions)){
      sEmotion <- emotions[iEmotion]
      dt_1_emotion_score <- dt_1[EmotionType %in% sEmotion]
      dt_2_emotion_score <- dt_2[EmotionType %in% sEmotion]
      t_test <- t.test(dt_1_emotion_score$Score_num, dt_2_emotion_score$Score_num, var.equal = FALSE)
      dt_ttest <- data.table(auction_1 = combs[iComb]$auction1,
                             time_obs_1 = combs[iComb]$time1,
                             auction_2 = combs[iComb]$auction2,
                             time_obs_2 = combs[iComb]$time2,
                             emotion = sEmotion,
                             mean_auction_1 = t_test$estimate[1],
                             mean_auction_2 = t_test$estimate[2],
                             t_stat = t_test$statistic,
                             p_value = t_test$p.value)
      dt_tttest <- dt_ttest[,auction_1_pct_auction_2 := ((mean_auction_1-mean_auction_2)/mean_auction_2)]
      l_emotions[[iEmotion]] <- dt_ttest
    }
    dt_emotions <- rbindlist(l_emotions, use.names = TRUE, fill=TRUE)
    l_combs[[iComb]] <- dt_emotions
  }
  dt_combs <- rbindlist(l_combs, use.names = TRUE, fill = TRUE)
  
  # Create tables to plot over
  
  l_dt_emotions <- list()
  for(iEmotion in 1:length(emotions)){
    sEmotion <- emotions[iEmotion]
    l_dt_emotions[[iEmotion]] <- dt_combs[emotion %in% sEmotion]
    dt <- l_dt_emotions[[iEmotion]]
    dt <- dt[order(-auction_1, time_obs_1, -auction_2, time_obs_2)]
    dt <- dt[, pstars:='']
    dt <- dt[p_value <= 0.01, pstars:='***']
    dt <- dt[p_value > 0.01 & p_value <= 0.05, pstars:='**']
    dt <- dt[p_value > 0.05 & p_value <= 0.10, pstars:='*']
    dt <- dt[ , s_val:=paste0(round(auction_1_pct_auction_2, 3), pstars)]
    dt <- dt[, s_val:=stringr::str_pad(s_val, 9, side='right', pad=' ')]
    dt_cast <- dcast(dt, auction_1 + time_obs_1 ~ auction_2 + time_obs_2, value.var='s_val')
    dt_cast <- dt_cast[, time_obs_1:=stringr::str_replace_all(time_obs_1, '(^[a-i]{1,1}\\_second)', '')]
    new_col_names <- sapply(names(dt_cast), function(x) stringr::str_replace(x, '(^dutch\\_[a-i]{1,1}\\_second)', ''))
    setnames(dt_cast, names(dt_cast), new_col_names)
    dt_cast$auction_1 <- NULL
    dt_cast$row_names <- c('$0-1$', '$1-2$', '$2-3$', '$3-4$', '$\\leq 2$' , '$\\leq 3$',  '$\\leq 4$')
    dt_cast <- dt_cast[, .(`row_names`, `0`, `1`, `2`, `3`, `lt2`, `lt3`, `lt4`)]
    setnames(dt_cast, 'row_names', '')
    l_dt_emotions[[iEmotion]] <- dt_cast
  }
  names(l_dt_emotions) <- emotions
  saveRDS(l_dt_emotions, dt_emotions_in_the_money_location)
} else {
  l_dt_emotions <- readRDS(dt_emotions_in_the_money_location)
  emotions <- names(l_dt_emotions)
}
## Latex table output
captions_text <- ' emotional response of value allocation by time'
captions <- paste0(emotions, captions_text)

l_body <- NULL
l_body <- list()

l_table <- list()
l_header_list <- as.character()
l_header_list[1] <- '\\begin{table}[!htb] \n'
l_header_list[2] <- '\\caption{Emotional Response to Auction Finish: Auction Type and Time Analysis (part 1/2)} \n'
l_header_list[3] <- '\\label{tab:emotionalResponse2} \n'
l_header_list[4] <- '\\centering \n'
l_header_list[5] <- '\\begingroup \n'
l_header_list[6] <- '\\scriptsize \n'
l_header_list[7] <- '\\begin{tabular}{lrrrrrrr} \n'
l_header_list[8] <- '\\toprule'
l_header_list[9] <- '\\emph{First Price} & \\multicolumn{7}{c}{\\emph{Dutch}} \\\\ \n'
l_header_list[10] <- '\\cmidrule(lr){2-8} \n & $0-1$ & $1-2$ & $2-3$ & $3-4$ & $\\leq 2$ & $\\leq 3$ & $\\leq 4$ \\\\ \n'  

l_table$header <- l_header_list

l_body <- list()
for(i in 1:5){
  body_header <- character()
  body_header[1] <- '\\cmidrule(lr){2-8} \n'
  body_header[2] <- paste0('& \\multicolumn{7}{c}{\\emph{Panel ', stringr::str_to_upper(letters[i]),
                           ': ', emotions[i], '}}\\\\ \n')
  body_header[3] <- '\\cmidrule(lr){1-1} \\cmidrule(lr){2-8}'
  
  body <- character()
  body <- print.xtable(xtable(l_dt_emotions[[i]], format='latex'), include.rownames=FALSE, sep='\n', print.results = FALSE)
  body <- as.character(stringr::str_split(body, '\\n', simplify = FALSE)[[1]])
  body <- body[c(9:15)]
  body <- stringr::str_replace_all(body, '\\\\(?=\\$)', '')
  body <- stringr::str_replace_all(body, '.+(?=leq)', '$\\\\')
  l_body[[i]] <- c(body_header, body)
}

l_table$body <- l_body  

body_footer <- character()
body_footer[1] <- '\\bottomrule \n'
body_footer[2] <- '\\end{tabular} \n'
body_footer[3] <- '\\begin{minipage}{\\textwidth}'
body_footer[4] <- '\\footnotesize'
body_footer[5] <- '\\vspace{0.25cm}'
body_footer[6] <- '\\emph{Notes:} Table Values represent (mean(first price emotion score)-mean(dutch emotion score))/mean(dutch emotion score). ***, **, *, for p-values of 0.01, 0.05, 0.10 for the hypothesis test that mean(first price emotion score)=mean(dutch emotion score)'
body_footer[7] <- '\\end{minipage}'
body_footer[8] <- '\\endgroup'
body_footer[9] <- '\\end{table}'

l_table$body_footer <- body_footer
table_out <- unlist(l_table)
knitr::raw_latex(table_out)

l_body <- NULL
l_body <- list()

l_table <- list()
l_header_list <- as.character()
l_header_list[1] <- '\\begin{table}[!htb] \n'
l_header_list[2] <- '\\caption{Emotional Response to Auction Finish: Auction Type and Time Analysis (part 2/2)} \n'
l_header_list[3] <- '\\label{tab:emotionalResponse} \n'
l_header_list[4] <- '\\centering \n'
l_header_list[5] <- '\\begingroup \n'
l_header_list[6] <- '\\scriptsize \n'
l_header_list[7] <- '\\begin{tabular}{lrrrrrrr} \n'
l_header_list[8] <- '\\toprule'
l_header_list[9] <- '\\emph{First Price} & \\multicolumn{7}{c}{\\emph{Dutch}} \\\\ \n'
l_header_list[10] <- '\\cmidrule(lr){2-8} \n & $0-1$ & $1-2$ & $2-3$ & $3-4$ & $\\leq 2$ & $\\leq 3$ & $\\leq 4$ \\\\ \n'  

l_table$header <- l_header_list

l_body <- list()
for(i in 6:length(captions)){
  body_header <- character()
  body_header[1] <- '\\cmidrule(lr){2-8} \n'
  body_header[2] <- paste0('& \\multicolumn{7}{c}{\\emph{Panel ', stringr::str_to_upper(letters[i]),
                           ': ', emotions[i], '}}\\\\ \n')
  body_header[3] <- '\\cmidrule(lr){1-1} \\cmidrule(lr){2-8}'
  
  body <- character()
  body <- print.xtable(xtable(l_dt_emotions[[i]], format='latex'), include.rownames=FALSE, sep='\n', print.results = FALSE)
  body <- as.character(stringr::str_split(body, '\\n', simplify = FALSE)[[1]])
  body <- body[c(9:15)]
  body <- stringr::str_replace_all(body, '\\\\(?=\\$)', '')
  body <- stringr::str_replace_all(body, '.+(?=leq)', '$\\\\')
  l_body[[i]] <- c(body_header, body)
}

l_table$body <- l_body  

body_footer <- character()
body_footer[1] <- '\\bottomrule \n'
body_footer[2] <- '\\end{tabular} \n'
body_footer[3] <- '\\begin{minipage}{\\textwidth}'
body_footer[4] <- '\\footnotesize'
body_footer[5] <- '\\vspace{0.25cm}'
body_footer[6] <- '\\emph{Notes:} Table Values represent  (mean(first price emotion score)-mean(dutch emotion score))/mean(dutch emotion score). ***, **, *, for p-values of 0.01, 0.05, 0.10 for the hypothesis test that mean(first price emotion score)=mean(dutch emotion score)'
body_footer[7] <- '\\end{minipage}'
body_footer[8] <- '\\endgroup'
body_footer[9] <- '\\end{table}'

l_table$body_footer <- body_footer
table_out <- unlist(l_table)
knitr::raw_latex(table_out)

```


