---
title: 'Memo: Value Allocation Response'
author: "Johnson"
date: "9/18/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
dt_seconds <- readRDS('~/Dropbox/pkg.data/auction_emotions/Clean/dt_seconds.rds')
```

# Background

This memo describes the auction emotion responses to the value allocation.

Analysis is as follows:

1. Emotional response to value allocation (not controlling for value) for 1, 2, 3, 4 seconds after the value allocation. (Including aggregate and snapshot seconds)
2. Emotional response to value allocation by Value quartile (and seconds in 1)
3. Emotional response to vlaue allocation regression with individual fixed effects.

# Emotion response to value allocation

```{r}

l_seconds_dts <- list()

l_seconds_dts$one_second <- dt_seconds[MarkerType=='auction' & marker_sec_elapsed <= 1 & !is.na(Score_num)]
l_seconds_dts$first_two_seconds <- dt_seconds[MarkerType=='auction' &
                                                 marker_sec_elapsed <= 2 &
                                                 !is.na(Score_num)][,Score_num:=mean(Score_num), 
                                                                    by=.(AuctionType, AuctionNumber, EmotionType, participant_id)]
l_seconds_dts$first_three_seconds <- dt_seconds[MarkerType=='auction' &
                                                 marker_sec_elapsed <= 3 &
                                                 !is.na(Score_num)][,Score_num:=mean(Score_num),
                                                                    by=.(AuctionType, AuctionNumber, EmotionType, participant_id)]
l_seconds_dts$first_four_seconds <- dt_seconds[MarkerType=='auction' &
                                                 marker_sec_elapsed <= 4 &
                                                 !is.na(Score_num)][,Score_num:=mean(Score_num),
                                                                    by=.(AuctionType, AuctionNumber, EmotionType, participant_id)]
l_seconds_dts$second_one <- dt_seconds[MarkerType=='auction' &
                                                 marker_sec_elapsed == 1 &
                                                 !is.na(Score_num)]
l_seconds_dts$second_two <- dt_seconds[MarkerType=='auction' &
                                                 marker_sec_elapsed == 2 &
                                                 !is.na(Score_num)]
l_seconds_dts$second_three <- dt_seconds[MarkerType=='auction' &
                                                 marker_sec_elapsed == 3 &
                                                 !is.na(Score_num)]
l_seconds_dts$second_four <- dt_seconds[MarkerType=='auction' &
                                                 marker_sec_elapsed == 4 &
                                                 !is.na(Score_num)]


# Create t-test
emotions <- unique(dt_first_two$EmotionType)
l <- list()
for(iEmotion in 1:length(emotions)){
  sEmotion <- emotions[iEmotion]
  t_test <- t.test(dt_first_two[AuctionType=='first_price' & EmotionType %in% sEmotion]$Score_num,
                   dt_first_two[AuctionType=='dutch' & EmotionType %in% sEmotion]$Score_num, var.equal = FALSE)
  dt_ttest <- data.table(emotion = sEmotion,
                         mean_first_price = t_test$estimate[1],
                         mean_dutch = t_test$estimate[2],
                         t_stat = t_test$statistic,
                         p_value = t_test$p.value)
  l[[iEmotion]] <- dt_ttest
}
    dt_emotion_first_two_seconds <- data.table::rbindlist(l, use.names=TRUE, fill=TRUE)
```
